A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-08 03_smoothing_tracks.Rmd
minor edit

### Robustness to Large Gaps

The median smooth is robust to large gaps in the data, and tracks do not need to be split when a large chunk of data are missing.
The easiest way to illustrate this is with a figure.

>>>>

We save the 11 point smoothed data.

```{r}
fwrite(list_of_smooths[[3]], file = "data/data_smooth.csv")
```

We prepare the data for plotting.
